\problemname{Elder Scrollbar}

When the first scrollbars appeared on resizable windows during user interface development in the Elder Days, computer graphics were still primitive.
Widgets were made with ASCII symbols and text was monospaced.
A window displayed a so-called \emph{viewport}, a part of a much longer text, adjusted to fit the width of the window.
A particularly innovative feature was the \emph{thumb}, shown as an X, which represented the position of the viewport relative to the full (adjusted) text and allowed vertical nagivation by clicking and dragging.

Alas, the knowledge of the Ancients has been lost in the Great Cataclysm, which destroyed the last remaining implementations of the user interface layer of the Elder GUI. 
As head programmer of the National Laboratory of Comparative User Interface Archeology it is your job to recreate the behaviour of those old machines as faithfully as possible.

Thanks to many years of studies, you have full understanding of the typographical aesthetics of the Elder Days:
Lines were set flush left but ragged-right, and exactly one space separated words on the same line. 
Line-breaking was simple in those days: When the next word of the text fit on the current line, it was put there, otherwise a new line was started.
If a word was too wide to fit the viewport, it was set on a line of its own and truncated at the right margin.

The language of the Ancients was written in upper- and lowercase letters of the English alphabet without punctuation or hyphenation.
The scroll bar on the right contained navigation widgets for ``up'' and ``down'' at the top and bottom. 
The relative position of the thumb corresponded to the relative position of the viewport in the adjusted text, rounded down.

Your researchers have collected countless old log files of calls to the window manager layer of the lost computers.

\section*{Input}

The first line conists of $4$ integers $W$, $H$, $L$, $N$, separated by a single space.
The width of the viewport is $W$, with $3\leq W\leq 200$.
The height of the viewport is $H$, with $3\leq H\leq 200$.
The viewport must show line $L$ of the width-adjusted input as the first line; the convention is that lines are numbered $0,\ldots, T-H$, where $T$ is the total number of lines in the width-adjusted text.
The following $N$ lines for $1\leq N\leq 10^5$ contain the text, at most 80~characters per line, including spaces; neither the first nor last character in each line are a space. 
No word in the language of the Ancients was more than 80~characters.


\section*{Output}

Print the window as the Ancients would have seen it, built from minus (\verb!-!), plus (\verb!+!), pipe (\verb!|!), lower-case V (\verb!v!), caret (\verb!^!), and upper-case X (\verb!X!).
See the sample output for the details.
The elder rules for rounding have been lost, so it does not matter if your X is off by one position in either direction.
